\input{title.tex}

### 2022-05-29 docs/papers/01_manuscript/04_discussion.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

% \subsection{CAUSES OF INSTITUTIONAL IMPACTS}
% \subsection{}
\label{discussion-1}
% discussion-1: 主要介绍结果的意义、合理性
In addition to quantitatively demonstrating the regulatory effect of 98-UBR by previous studies, our study also found that 87-WAS would increase overall water use of the YRB.
The results challenged the previous analyses (who suggested that the 87-WAS ``has little effect'') because the difference between prediction and observation will be trivial when the institutional shift was just a blank policy by applying the DSC method \cite{abadie2015,hill2021}.
Fixing the environmental background, the forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textbf{methods} and \textit{Appendix~\nameref{secS2}}).
After 87-WAS, the growth of economic volume (both in agriculture, industry and services) in the YRB broke the parallel trend with other regions since 1975 (\textit{Appendix S3} Figure~\ref{fig:variables}), though domestics water and environmental context remained their trends.
Furthermore, construction of water-saving facilities (especially in agriculture) after the 87-WAS may contribute to the water use changing per unit of production (\textit{Appendix~\nameref{secS3}}~Figure~\ref{fig:variables}).
These facts of saving water and speeding up water use simultaneously, are in line with the sigh from then: the tragedy of frequently scrambling for water appeared in some provinces \cite{mao2000}.
Since the 98-UBR improved tragedy of water competition greatly by water licences, therefore, many studies attributed the restoration from river depletion mainly to the successful institutional shift \cite{chen2021,huangang2002,an2007}.

% 过去的研究总结出87-WAS收效甚微的几个因素：
Although previous studies summarised reasons for the non-ideal effect of 87-WAS \cite{huangang2002}, few chanegs of those aspects in the 98-UBR indicate that influences from the structural changes were underestimated.
As we have depicted in Figure~\ref{structure}, the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

% \subsection{Linking structures with ISs outcomes}
\label{discussion-2}
% discussion-2: 机制解释
% 经济模型与理论解释
Differences in the pattern of the response by provinces can demonstrate the influence of social-ecological structures led by the institutional shifts.
We analyzed mathematically why the mismatched structure made limited water use holistically elusive in the institution shift of the 87-WAS but finally achieved by the 98-UBR (Figure~\ref{fig:model} and \textit{Appendix S4}).
By taking the structure before and after the two institutional shifts as different basic assumptions (before 87-WAS: free access to water; after 87-WAS but before 98-UBR: decisions on water use under quotas; after 98-UBR: unified regulation), we use the marginal benefit model to analyze the theoretical optimal water consumption of stakeholders in each scenario.
The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes.
Before the 98-UBR, the model assumes that the separated ecological units (river reaches) link to stakeholders (related provinces) who use water to pursue their marginal benefits but have a potential political cost if they exceed the quota 87-WAS.
Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (\textit{Appendix~\nameref{secS4}}).
Therefore, isolated stakeholders reacted to the similar marginal cost, and smaller water users have a threshold because of the political cost, so 87-WAS triggered an increased water use for the significant users.
On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs holistically as stakeholders only take corresponding responsibilities (follow the quota as possible as they can) to the YRCC (\textit{Appendix~\nameref{secS4}}).
As a result, unified regulating acted the core role after the 98-UBR and reduced water use of all stakeholders (provinces) by irregular ratios.

The alignments of differences in institutional structures and outcomes here echo the hypothesis that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders (in the YRB cases, through administration).
When links The water quotas of 87-WAS (or the initial water rights) in our case studies went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
The bargaining itself was also a process towards matches between their economic volume and water shares, as studies show that the large water users (like Shandong and Henan) need more water than their quota (in the 87-WAS) if only considering the economic equity when designing the institution.
Furthermore, with information asymmetry between upper-level decision-makers and lower-level stakeholders in water use allocation, those with more current water use might have greater bargaining power.
In practice, therefore, although the affected provinces may not have directly encouraged excessive resource use because of the institutional shift, they had a more considerable incentive to show their economic potential
That aligns with the historical records that, even after the 87-WAS had already confirmed the quotas, provinces, especially water-intensive ones, challenged it by appearing to the higher central government for larger quotas.
On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment, \textit{Supplementary Material S3})
\cite{krieger1955, ostrom1990}.
Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
The 98-UBR led to a structure for achieving social-ecological fits in both basins (between YRCC and the YRB) and regions (between provincial economy and their water shares).

@@

Matching social and ecological scales appears widespread as building blocks (or motifs) in successfully governed SES, whether in fisheries, forests, or groundwater management.
Since the building blocks introduced by 87-WAS and 98-UBR are recurring motifs in many SES, our proposed mechanism is crucial to understanding such coupled systems.
We explored these causal linkages between the SES structures and sustainability (outcomes) by quasi-natural experiments (the institutional shifts) of the YRB, which provides an informative case study for two main reasons.
First, different from gradual changes following bottom-up emergence, the top-down institutional shifts induced sharp changes in SES structures in the YRB, enabling us to estimate their net effects quantitatively.
Second, as few basins experienced such radical institutional shifts more than once, the YRB provides comparable settings for understanding the impacts of structural changes in SESs.
However, one of the inevitable limitations of our method is that it is difficult to rule out the effects of other policies over the same time breakpoints.
Since scholars have reached a consensus on the importance of the two institutional shifts of 87-WAS and 98-UBR, the differences in their results still provide important insights for understanding water governance.

% 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure (isolated stakeholders with the fragmentation of ecology) is not conducive to institutional solutions.
Moreover, we report how another institutional shift contributed to successful water governance  -the subsequent success of 98-UBR has proved the importance of social-ecological fit again, theoretically and practically.
For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system (in this case, the basinal scale and the YRCC).
From these starting points, several other scenarios given by a marginal benefit model (see \textit{Supplementary Material S4}) can provide plausible insights into water governance.
For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential to result in better water governance.
In addition, the policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to respond to changing SES context.

% 未来的政策建议
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions to sustainability (see \textit{Appendix \nameref{secS1}}) \cite{yu2019}.
Given recent changes in the YRB, outdated and inflexible water quota can no longer meet the new demands of economic development \cite{wang2019a}.
As a result, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{Appendix~\nameref{secS1}}).
These initiatives can benefit from our analysis by actively incorporating social-ecological matched building blocks when developing a new institutional shift toward sustainability.
Moreover, our research provides a cautionary tale of how institutions can be double-edged, while insights from the YRB can be a valuable guideline for SESs worldwide \cite{cumming2020b, muneepeerakul2017, cumming2020a, leslie2015}.

>>>>

% \subsection{CAUSES OF INSTITUTIONAL IMPACTS}
% \subsection{}
\label{discussion-1}
% discussion-1:
% 用水量的上升、下降-结果解读
We quantitatively demonstrated that the 98-UBR decreased, but the 87-WAS increased YRB's water use.
The results challenged the previous analyses (they used to suggest that the 87-WAS ``has little practical effect'') because theoretically, the DSC method would show few differences between estimation and observation for a blank policy \cite{abadie2015,hill2021}.
However, the significant net effect suggests the institutional shift (87-WAS) followed by backfired more water use even after controlling the environmental and economic variables (see \textit{Appendix~\nameref{secS2}}~Table~\ref{tab:variables}).
The speeding up water use aligns with the sigh from then: the tragedy of frequently scrambling for water appeared in some provinces \cite{mao2000}.
On the contrary, 98-UBR reduced the tragedy of water competition considerably by water licenses, so many studies attributed the restoration from river depletion mainly to the successful institutional shift \cite{chen2021,huangang2002,an2007}.

% 我们认为制度结构的变化是被长期忽略的重要因素
We proposed that for these institutional shifts' divergent outcomes regarding water use, the key factors long ignored can be institutional structure changes.
The structural building blocks we depicted in Figure~\ref{structure}, which were also reported in various types of SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}, and here twice reframed by the institutional shifts.
Before the 98-UBR, the SES structure (i.e., fragment ecological units are linked to separate social actors) is more likely to be mismatched because isolated actors generally struggle with holistically maintaining interconnected ecosystems \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
On the contrary, institutional alignments since the 98-UBR improved YRCC's authority in water use regulation to match the YRB in scale, thus leading to social-ecological fit and good outcomes -a ``scale-matched'' example \cite{cumming2020a,wang2019d}.
Despite other reasons for the non-ideal effect of the 87-WAS being widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), few radical improvements in the 98-UBR suggest an over-attention paid to non-structural impacts.

% \subsection{Linking structures with ISs outcomes}
\label{discussion-2}
% discussion-2: 机制解释
Different individual provinces' water-use responses to the institutional shifts also support influences from SES structures.
Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS.
This ``major users use more'' pattern supports the hypothesis that separated stakeholder (individual province here) decides on linked ecological units for output maximization (water use).
Therefore, we theoretically abstracted the structures associated with the structural changes induced and analyzed how different water allocation structures shape different outcomes.
Assuming that water is the factor input with decreasing marginal output of each province, we discuss the marginal return and optimal water use under three different cases (analogy to Figure~\ref{structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{Appendix~\nameref{secS4}}).
The incentive for water overuse (compared to the water quotas) in each province derives from the mismatch between the benefits and costs of water use.
Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive of water use, leading to higher water use.
Therefore, the water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under the unified allocation.
Our model interprets the results from structural perspectives: excessive water use incentive induces the acceleration of extracting resources for future economic growth, and a unified institution is indispensable for sustainable water use.

\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.9\linewidth]{outputs/economic_model.pdf}
	\caption{
		\textbf{A.} The relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
	\label{fig:model}
\end{figure}

% The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022}, which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
Our above theoretical discussion also aligns with the evolution of the institutions in the YRB.
When links The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
The bargaining was also a process for matching their water shares to economic volume because the major water users (like Shandong and Henan) need more water than their quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
Furthermore, those with more current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligns with the fact that they appeared to the higher central government for larger shares \cite{wang2019a, wang2019d}.
On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
\cite{krieger1955, ostrom1990}.
Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.

@@

We explored these causal linkages between the SES structures and sustainability (outcomes) by quasi-natural experiments (the institutional shifts) of the YRB, which provides a unique case for two main reasons:
(1) The top-down institutional shifts induced sharp changes in SES structures in the YRB, enabling us to estimate their net effects quantitatively.
(2) Since few basins experienced such radical institutional shifts more than once, the YRB provides comparable settings for understanding the structural changes of SESs.

In complex coupled human-nature systems, however, our approach also has inevitable limitations:
(1) The contributions of economic growth and institutional shifts are still incomparable because of intertwined causality (institutional changes can also influence the relative economic variables).
Still, our quasi-experiment approach focused on and proved that a change in water use trajectory follows the YRB's unique institutional shifts.
(2) When applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
However, since the analysis had agreed on the importance of the two institutional shifts of 87-WAS and 98-UBR in water governance \cite{wang2012b}, our results on their effects still provide insights for understanding water governance.

% 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
Our results and discussion deepen the understanding of SES structure and strengthen the basic knowledge that the mismatched structure (isolated stakeholders with the fragmentation of ecology) is not conducive to institutional solutions \cite{bodin2017b, ostrom2009, reyers2018}.
Moreover, we report how another structure contributed to successful governance -the subsequent success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit again.
For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system.
From these perspectives, we give two scenarios based on the marginal benefit model (see \textit{Appendix \nameref{secS5}}), which can inspire institutional design on how to reduce mismatches.
For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential to result in better water governance.
In addition, the policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to respond to changing SES context \cite{reyers2018}.

The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions to sustainability (see \textit{Appendix \nameref{secS1}}) \cite{yu2019}.
Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019a}.
Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{Appendix~\nameref{secS1}}).
These initiatives can benefit from our analysis by actively incorporating social-ecological matched building blocks when developing a new institutional shift for sustainability \cite{bodin2017b}.
Moreover, our research provides a cautionary tale of how institutions can be double-edged \cite{hegwood2022}, while insights from the YRB can be a valuable guideline for SESs worldwide \cite{muneepeerakul2017, leslie2015}.

### 2022-05-29 docs/papers/01_manuscript/05_conclusion.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

Intense water use in one of the most anthropogenic interfered large river basins, the Yellow River Basin (YRB), once led to overburdened drying up but finally had a successful restoration by sequential water governance practices.
Focusing on two water-demand institutions, 87-WAS and the 98-UBR, we quantitatively analyzed how institutional shifts played a role in the water governance achievement of the YRB.
Shifting throughout different SES structures framed by them, the observed water use of the YRB provinces had an $8.57\%$ increase than expected during the decade after the 87-WAS.
Then, water use significantly decreased by  $4.9 billion m^3$ per year since the 98-UBR, while the model still suggests a $10.3 billion m^3$ annual increase in expectation.
Finally, as differences in stakeholders' response to the institutional shifts, water use rises after the 87-WAS in provinces with more water uses (e.g., Inner Mongolia, Henan, and Shandong) while shrunk in nearly all provinces after the 98-UBR.
Since the above results closely align with interpretations from a mathematical marginal benefits model, we can link the structures (widespread building blocks) and outcomes (goals of the institution, i.e., limiting water demands) by these quasi-natural experiments of the YRB.
We demonstrate that social-ecological fits lead to successful governance where reducing independent stakeholders linked to fragmentation is an essential primary mechanism for good SES outcomes.

>>>>

Intense water use in one of the most anthropogenic interfered large river basins, the Yellow River Basin (YRB), once led to overburdened drying up but finally had a successful restoration by sequential water governance practices.
Focusing on two water-demand institutions (87-WAS and the 98-UBR), we quantitatively analyzed how institutional shifts played a role in the water governance achievement of the YRB.
Shifting throughout different SES structures framed by them, the observed water use of the YRB provinces had a $6.57\%$ increase than expected during the decade after the 87-WAS.
Then, water use significantly decreased by $0.49$ billion $m^3$ per year since the 98-UBR, while the model still suggests a $0.82$ billion $m^3$ annual increase in expectation.
Finally, as differences in stakeholders' response to the institutional shifts, water use rises after the 87-WAS in provinces with more water uses (e.g., Inner Mongolia, Henan, and Shandong) while shrunk in nearly all provinces after the 98-UBR.
Since the above results closely align with interpretations from a mathematical marginal benefits model, we can link the structures (widespread building blocks) and outcomes (goals of the institution, i.e., limiting water demands) by these quasi-natural experiments of the YRB.
We demonstrate that social-ecological fits lead to successful governance where reducing independent stakeholders linked to fragmentation is an essential primary mechanism for good SES outcomes.

### 2022-05-29 docs/papers/01_manuscript/06_methods.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
We first abstract the SES structures of water using in the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces. We then estimated the net effects of two institutional shifts on total water uses, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}. For the stability of DSC model, we use Principal Components Analysis (PCA) method to reduce the dimensionality of many variables affecting the total water use. Finally, for discussion, we created an economic model based on marginal revenue to provide the observed water use changes a theoretical interpretation.

@@

\subsection{Portraying structures}
% 制度结构关系抽象
We apply network approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), govern unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
For example, institutions may create a horizontal connected structure that encourages collaboration between the different stakeholders managing ecological components (Figure~\ref{framework} c).
Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating through the higher-level governing node (Figure~\ref{framework} d).
Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and a network-based description is a widely used way to depict them by abstracting links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details), in which the agents are abstracted as nodes and the required interactions between agents are abstracted as links.
The resulting structure is mainly used to inference the mechanism of institutional impact in the discussion, and to give an overview understanding of the institutional shifts.
We try to approve that focusing on SES structures rather than institutional details, can well interpret the differences caused by institutional shifts in the YRB, and keeps consistent with previous studies theoretically.

\subsection{Differenced Synthetic Control}
We estimate water use without institutional shifts effect by using the Differenced Synthetic Control (DSC) method.
The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
This method aims to evaluate the effects of policy change that are not random across units but focus on some of the units (i.e., institutional shifts in the YRB here).
By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated unit(s) by constructing a synthetic version of the treated unit(s) equal to a convex combination of control units with a new estimator with improved bias properties.

In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1979-1998; 1987-2008.
We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied \cite{abadie2021}.
Then, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
We define $T_0$ to represent the number of pre-treatment periods ($1,\cdots,t_0$) and $T_1$ the number post-treatment periods ($t_0,\cdots,T$), such that $T = T_0+ T_1$.
That is, treated unit is exposed to the institutional shift in every post-treatment period $T_0$, and unaffected by the institutional shift in all preceding periods $T_1$.
Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1},...,w_{J})$, with $w_j \in (0, 1)$.
Among them, by introduce a ($k * k$) diagonal, semidefinite matrix $\mathbf{V}$ that signifies the relative importance of each covariate, the DSC method procedure for finding the optimal synthetic control ($W$) is expressed as follows:

@@

where $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$. That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W*(V)}$. We choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:

@@

That is the minimum difference between the outcome of the treated unit and the synthetic control in the pre-treatment period, where $\mathbf{Z}_{1}$ is a ($1*T_0$) matrix containing every observation of the outcome for the treated unit in the pre-treatment period. Similarly, let $\mathbf{Z}_{0}$ is a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, $k$ is number of variables in the datasets.
The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties \cite{billmeier2013, smith2015}.

\subsection{Dataset and preprocessing}\label{sec:dataset}
We choose dataset and variables to compare on actural and estimated water use of the YRB.
The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020) \cite{zhou2020}.
To estimate the water use of the YRB by assuming there were not effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors. Their specific items and origins are listed in Table~\ref{tab:variables}.

Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing because their trivial water use from the YRB (see \textit{Appendix}~Table~\ref{tab:quota}). We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$, for applying the DSC.

Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ pricipal components Appendix~\nameref{secS3}. Bayan had proved that combining PCA and DSC can rise robustness of causal inference \cite{bayani2021}. Here, we first applied the Zero-Mean normalization (unit variance), as the variables' unit are far different. We use Elbow method to choose number of the pricipal components, as Appendix~\nameref{secS3}~Figure~\ref{fig:elbow} shows, $5$ components well reduced the dimensions of the dataset with $89.63\%$ variance explaination.

\subsection{Economic model}\label{sec:model}
In order to inference the mechanisms underlying the results, we developed a economic model based on marginal revenue to analyze how institutional shift could have led to differences in water use.

@@

\begin{ass}
    (Multi-period settings) There are multiple settings periods with a constant discount factor for expectation of future water use.
\end{ass}

Under the above simplified assumptions, we demonstrate three cases -corresponding the abstracted SES structures (Figure~\ref{structure}), inference how SES structure alters the expected marginal benefits and costs of provinces making decisions.
As one of the possible interpretation for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

>>>>

% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
We first abstract the SES structures of water used in the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces.
For preprocessing the data, we use Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
We then estimated the net effects of two institutional shifts on total water use, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}.
Finally, for discussion, we created an economic model based on marginal revenue to provide the observed pattern of water use changes with a theoretical interpretation.

@@

\subsection{Portraying structures}\label{sec:structures}
% 制度结构关系抽象
We apply the network \cite{bodin2017b} approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and the network-based approach is to abstract connections between entities into links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details).
Besides the ecologically connected river reaches, the agents (provinces and the YRCC) are abstracted as nodes, and their required interactions regarding water use are summarized as links.
The 1987-WAS requires the YRCC to monitor each river's reach, while the 1998-UBR requires direct interactions (through water use licenses) between the YRCC and the provinces.
Therefore, we linked the YRCC unit to each ecological unit after 87-WAS and each province unit after the 98-UBR.
We try to approve that focusing on SES structures rather than institutional details can reasonably interpret the differences caused by institutional shifts in the YRB.

\subsection{Dataset and preprocessing}\label{sec:dataset}
We choose datasets and variables to compare on actual and estimated water use of the YRB.
The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020) \cite{zhou2020}.
To estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors. Their specific items and origins are listed in Table~\ref{tab:variables}.

Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin, and Beijing because of their trivial water use from the YRB (see \textit{Appendix}~Table~\ref{tab:quota}). We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$ for applying the DSC.

Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components \textit{Appendix~\nameref{secS2}}. Bayan had proved that combining PCA and DSC can raise the robustness of causal inference \cite{bayani2021}. We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different. Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure~\ref{fig:elbow}}). Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.

\subsection{Differenced Synthetic Control}\label{sec:DSC}
We estimate water use without institutional shifts effect using the Differenced Synthetic Control (DSC) method.
The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.

This method aims to evaluate the effects of policy change that are not random across units but focuses on some of them (i.e., institutional shifts in the YRB here).
By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated unit(s) by constructing a synthetic version of the treated unit(s) equal to a convex combination of control units.
Therefore, the synthetic and actual version difference can be estimated as a net effect for a treated unit.

In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1979-1998; 1987-2008.
We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied \cite{abadie2021}.
Then, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
We define $T_0$ to represent the number of pre-treatment periods ($1,\cdots,t_0$) and $T_1$ the number post-treatment periods ($t_0,\cdots,T$), such that $T = T_0+ T_1$.
The treated unit is exposed to the institutional shift in every post-treatment period $T_0$, unaffected by the institutional shift in all preceding periods $T_1$.
Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1},...,w_{J})$, with $w_j \in (0, 1)$.
Among them, by introduce a ($k * k$) diagonal, semidefinite matrix $\mathbf{V}$ that signifies the relative importance of each covariate, the DSC method procedure for finding the optimal synthetic control ($W$) is expressed as follows:

@@

where $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$. That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W*(V)}$. Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:

@@

That is the minimum difference between the outcome of the treated unit and the synthetic control in the pre-treatment period, where $\mathbf{Z}_{1}$ is a ($1*T_0$) matrix containing every observation of the outcome for the treated unit in the pre-treatment period. Similarly, let $\mathbf{Z}_{0}$ be a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties \cite{billmeier2013, smith2015}.

\subsection{Economic model}\label{sec:model}
To infer the mechanisms underlying the results, we developed an economic model based on marginal revenue to analyze how the institutional shift could have led to differences in water use.

@@

\begin{ass}
    (Multi-period settings) There are multiple settings periods with a constant discount factor for the expectation of future water use.
\end{ass}

Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.
